### 2014-10-31 paper/include/dtail.tex
iFinished! yaya!

Cui et al. \cite{dtail} propose DTail. They evaluate two versions of DTail referenced as DTail-R and DTail-V utilizing R and V information, respectively. Even so, their main idea is that more types of  information can be incorporated and stored together with the R and V information. DTail can then choose the most efficient refresh schema depending on the current situation, i.e. workload and type of application. How acquisition of the \textit{refresh data} is to be performed is left as future work. Refresh data is kept per row and is stored in the DRAM itself instead of in the MC which many other solutions do \cite{raidr}\cite{smartrefresh}\cite{refrint}. To counter the added latency of a slower memory (DRAM versus fast memory in the MC), Cui et al. utilizes spatial locality of the RV information and performs prefetching into a FIFO buffer. As the refresh data is kept on a row level DTail can save more refreshes than other techniques that have a lower granularity.

>>>>

Cui et al. \cite{dtail} propose DTail. They evaluate two versions of DTail referenced as DTail-R and DTail-V utilizing R and V information, respectively. Even so, their main idea is that more types of  information can be incorporated and stored together with the R and V information. DTail can then choose the most efficient refresh schema depending on the current situation, i.e. workload and type of application. The R and V information, called\textit{refresh data}, is kept per row and is stored in the DRAM itself instead of in the MC which many other solutions do \cite{raidr}\cite{smartrefresh}\cite{refrint}. To counter the added latency of a slower memory (DRAM versus fast memory in the MC), Cui et al. utilizes spatial locality of the RV information and performs prefetching into a FIFO buffer. As the refresh data is kept on a row level DTail can save more refreshes than other techniques that have a lower granularity. How to actually implement the acquisition of the \textit{refresh data} is not stated, but Cui et al. proposes that a few modifications to the OS would work well, as the OS can manage the refresh data residing in DRAM.
